Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}

### 2020-06-04 paper-v1.tex
add tech points + test solidity smart contract + cleanup

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}

@@

@@

\section{Conclusion and Discussions}
In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain ecosystem.

\section{Supplementary material}
The source code is open and available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\input{solidity-highlighting.tex}	% copy the file from this repo
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304} \and
Nazzareno Massari\inst{2,3}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Polytechnic of Turin\\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Peer-review \and Privacy \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}

@@

\subsubsection{Bounty}

\begin{lstlisting}[language=Solidity]
pragma solidity 0.4.16;

contract TestContract {

	string private myString = "foo";

	function getString() constant returns (string) {
	    return myString;
	}

	function setString (string _string) {
	    myString = _string;
	}
}
\end{lstlisting}

\subsubsection{Token Economics}

\subsubsection{Quadratic Funding}

\subsubsection{Privacy}

\subsubsection{DAO}

@@

\section{Conclusion and Discussions}
In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.

\section{Supplementary material}
Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.
